---
title: "Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

# Load packages and data

```{r include=FALSE}
library(flexdashboard)

library(tidyverse)
library(plotly)
library(p8105.datasets)

data("rest_inspec")

```

Data cleaning

```{r}rest_inspec_year <- rest_inspec |>
  janitor::clean_names() |>
  separate(inspection_date, into = c("year", "month", "day"), sep = "-")
  
rest_inspec_filtered <- rest_inspec_year |>
  filter(year>=2013) |>
  group_by(boro, year) |>
  mutate(average_score = mean(score, na.rm = TRUE))


```

Cleaned names, separated inspection_date variable into day, month, and year, and filtered to only years 2013 and after in order to narrow down the dataset a bit. Also added a variable for average score for each borough each year.

Column {data-width=600}
-----------------------------------------------------------------------

### Restaurant Inspection Score by Borough, 2013-2017

```{r}
rest_inspec |>
  sample_n(size = 10000, replace = TRUE) |>
  filter(boro != "Missing") |>
  plot_ly(x= ~inspection_date, y = ~score, color= ~boro, type="scatter", marker = list(size = 3, opacity = 0.5))

```

Column {data-width=400}
-----------------------------------------------------------------------

### Average Restaurant Inspection Score by Borough, 2013-2017

```{r}
rest_inspec_filtered |>
  filter(boro != "Missing") |>
  plot_ly(y = ~score, color = ~ boro, type = "box")

```

### Number of Restaurants of Various Cuisine Types by Borough

```{r}
rest_inspec_filtered |>
  filter(cuisine_description %in% c("American", "Italian", "Korean", "Thai", "Chinese", "Seafood", "Portuguese", "Mediterranean", "Sandwiches", "Spanish", "African", "Irish", "Mexican", "Delicatessen")) |>
    filter(boro != "Missing") |>
  plot_ly(x = ~cuisine_description, color = ~boro, type = "histogram")
```