---
title: "Plotly"
output: 
  html_document:
    toc: true
    toc_float: true
---

We're making interactive plots


```{r include=FALSE}
library(tidyverse)
library(plotly)
library(p8105.datasets)
```


```{r INCLUDE=FALSE}
data("instacart")

instacart = 
  instacart |> 
  as_tibble()
```
```
Lets make a bar plot!
The bar plot shows number of items ordered in each aisle!
```{r}
instacart |> 
  count(aisle) |> 
  filter(n > 10000) |> 
  mutate(aisle = fct_reorder(aisle, n)) |> 
  ggplot(aes(x = aisle, y = n)) + 
  geom_bar(stat = "identity", fill = "blue") +  # Use geom_bar for bars
  labs(title = "Number of items ordered in each aisle") +
  theme(axis.text.x = element_text(angle = 60, hjust = 1))

```


Lets make a line graph of average number of orders per day of the week!

```{r}
avg_orders_per_day <- instacart |>
  group_by(order_dow) |>
  summarize(avg_orders = n() / n_distinct(order_id))

# Create a line graph
line_graph <- ggplot(avg_orders_per_day, aes(x = order_dow, y = avg_orders, group = 1)) +
  geom_line() +
  geom_point() +
  labs(title = "Average Number of Orders per Day of the Week",
       x = "Day of the Week",
       y = "Average Number of Orders")

# Show the line graph
print(line_graph)
```


Lets make box and whiskers plots that shows the order hours of day per day of the week!
```{r}
boxplot <- instacart |>
  ggplot(aes(x = factor(order_dow), y = order_hour_of_day)) +
  geom_boxplot() +
  labs(title = "Box and Whisker Plot of Order Hours per Day of the Week",
       x = "Day of the Week",
       y = "Order Hour of Day")

# Show the box and whisker plot
print(boxplot)
```
