---
title: "Plots"
output: 
  html_document:
    toc: true
    toc_float: true
---

We're making interactive plots


```{r include=FALSE}
library(tidyverse)
library(plotly)
library(p8105.datasets)
```


```{r INCLUDE=FALSE}
data("instacart")

instacart = 
  instacart |> 
  as_tibble()
```
```
Lets make a bar plot!

The bar plot shows number of products ordered in each aisle!
```{r}
  instacart |> 
  count(aisle) |> 
  mutate(aisle = fct_reorder(aisle, n)) |> 
  plot_ly(x = ~aisle, y = ~n, color = ~aisle, type = "bar", colors = "viridis")

```


Lets make a line graph of average number of orders per day of the week!

```{r}
plot_ly(data = avg_orders_per_day, x = ~order_dow, y = ~avg_orders, type = 'scatter', mode = 'lines+markers') %>%
  layout(title = "Average Number of Orders per Day of the Week",
         xaxis = list(title = "Day of the Week"),
         yaxis = list(title = "Average Number of Orders"))

```


Lets make box and whiskers plots that shows the order hours of day per day of the week!
```{r}
instacart |>
  mutate(order_dow = reorder(order_dow, order_hour_of_day)) |>
  plot_ly(y = ~order_hour_of_day, color = ~order_dow, type = "box", colors = "viridis")
```

